First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2016-09-06 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
added ALU(90 deg) plots for Q.2.a.ii

    \begin{figure}[tbp]
       \centering
    \includegraphics[height=8.6cm]{fig/ALU_coherent_MM2.pdf}
    \caption{The integrated coherent beam-spin asymmetries as a function of 
    $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ missing mass 
 squared.}
    \label{fig:exc_coh-alu}
    \end{figure}

@@

    \begin{figure}[tbp]
       \centering
    \includegraphics[height=8.6cm]{fig/ALU_incoherent_MM2.pdf}
    \caption{The integrated incoherent beam-spin asymmetries as a function of 
    $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ missing mass 
 squared.}
    \label{fig:exc_incoh-alu}
    \end{figure}

>>>>

    \begin{figure}[tbp]
    \includegraphics[height=6.0cm]{fig/ALU_coherent_MM2.pdf}
    \includegraphics[height=6.0cm]{fig/ALU_coherent_MM2_90deg.pdf}
    \caption{On the left: the integrated coherent beam-spin asymmetries as a 
    function of $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ 
 missing mass squared. On the right: $A_{LU}$ at 90$^{\circ}$ from fitting the
  reconstructed asymmetries as a function of the cut width.}
    \label{fig:exc_coh-alu}
    \end{figure}

@@

    \begin{figure}[tbp]
    \includegraphics[height=6.0cm]{fig/ALU_incoherent_MM2.pdf}
    \includegraphics[height=6.0cm]{fig/ALU_incoherent_MM2_90deg.pdf}
    \caption{On the left: the integrated incoherent beam-spin asymmetries as a 
    function of $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ 
 missing mass squared. On the right: $A_{LU}$ at 90$^{\circ}$ from fitting the 
 reconstructed asymmetries as a function of the cut width.}
    \label{fig:exc_incoh-alu}
    \end{figure}

### 2016-09-06 eg6-letters/coherent/HeliumCohDVCS.tex
added ALU(90 deg) plots for Q.2.a.ii

\begin{abstract}
We report the first exclusive measurement of deeply virtual Compton scatterring 
(DVCS) off a nuclei with the CLAS detector at the Jefferson laboratory. The 
observed beam spin asymmetries are significantly larger than for proton, 
confirming expectations from plane wave impulse approximation. We present an 
extraction of the unique generalized parton distribution (GPD) of the spin-0 
helium in a completely model independent way. This result demonstrate the 
strength of the method and opens a new unique access into nuclei 3D structure 
in term of quarks and gluons.
\end{abstract}

>>>>

\begin{abstract}
We report the first exclusive measurement of deeply virtual Compton scattering 
(DVCS) off a nuclei with the CLAS detector at the Jefferson laboratory. The 
observed beam spin asymmetries are significantly larger than for proton, 
confirming expectations from plane wave impulse approximation. We present an 
extraction of the unique generalized parton distribution (GPD) of the spin-0 
helium in a completely model independent way. This result demonstrate the 
strength of the method and opens a new unique access into nuclei 3D structure 
in term of quarks and gluons.
\end{abstract}
